### 2020-05-28 myThesis/thesis_LaTeX/Chapters/1.tex
thesis re-organisation

\chapter{Carbon nanowires research developments in terms of published papers, synthesis and production} % Main chapter title

@@

%----------------------------------------------------------------------------------------
%	SECTION 1
%----------------------------------------------------------------------------------------
\section{}

Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

>>>>

\chapter{Introduction} % Main chapter title

@@

%----------------------------------------------------------------------------------------
%	SECTION 1
%----------------------------------------------------------------------------------------
\section{Problem definition and motivation}

%Qué metodos se han utilizado? (SU-8)
%Porqué se quiere fabricar las fibras de carbono
%Para qué aplicaciones se han usado
%Porqué es importante la conductividad
%Porqué es importante que sea puro carbono

%----------------------------------------------------------------------------------------
%	SECTION 2
%----------------------------------------------------------------------------------------
\section{Research Questions}

%----------------------------------------------------------------------------------------
%	SECTION 3
%----------------------------------------------------------------------------------------
\section{Hypothesis}

%----------------------------------------------------------------------------------------
%	SECTION 4
%----------------------------------------------------------------------------------------
\section{Objectives}

%----------------------------------------------------------------------------------------
%	SECTION 5
%----------------------------------------------------------------------------------------
\section{Dissertation Outline}

### 2020-05-28 myThesis/thesis_LaTeX/Chapters/2.tex
thesis  structure
thesis re-organisation

\chapter{Carbon nanowires research developments in terms of published papers, synthesis and production} % Main chapter title

\label{Chapter:1}

@@

Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

>>>>

\chapter{Carbon Nanowires Research Developments in Terms of Published Papers, Synthesis and Production} % Main chapter title

\label{Chapter:2}

@@

### 2020-05-28 myThesis/thesis_LaTeX/Chapters/3.tex
thesis  structure
thesis re-organisation

\chapter{Fabrication Process Selection of Conductive Carbon Nanowires} % Main chapter title

\label{Chapter:2}

%----------------------------------------------------------------------------------------
%	SECTION 1
%----------------------------------------------------------------------------------------
\section{}

Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

>>>>

\chapter{Near-Field Electrospinning as an Affordable Way to Gain Spatial Control} % Main chapter title

\label{Chapter:3}

%----------------------------------------------------------------------------------------
%	SECTION 1
%----------------------------------------------------------------------------------------
\section{Review of Polymer Solutions for NFES with Spatial Control}

### 2020-05-28 myThesis/thesis_LaTeX/Chapters/4.tex
thesis  structure
thesis re-organisation

\chapter{Near-Field Electrospinning as an Affordable Way to Gain Spatial Control} % Main chapter title

\label{Chapter:3}

%----------------------------------------------------------------------------------------
%	SECTION 1
%----------------------------------------------------------------------------------------
\section{}

Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

>>>>

\chapter{Compatible Polymer-Solvent Combinations for Near-Field Electrospinning and Pyrolysis} % Main chapter title

\label{Chapter:4}

%----------------------------------------------------------------------------------------
%	SECTION 1
%----------------------------------------------------------------------------------------
\section{Design and Selection of Candidate Spunable Polymer Solutions}

%high molecular weight, polymer-solution interaction (straight chains)

\subsection{Rheology of candidate polymer solutions}

%----------------------------------------------------------------------------------------
%	SECTION 1
%----------------------------------------------------------------------------------------
\section{Effect of aromatic groups in oxygen-free polymers in NFES and Pyrolysis}

### 2020-05-28 myThesis/thesis_LaTeX/Chapters/5.tex
thesis  structure
thesis re-organisation

\chapter{Compatible Polymer-Solvent Combinations for Near-Field Electrospinning} % Main chapter title

\label{Chapter:4}

@@

Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

>>>>

\chapter{Fabrication of Polymeric Fibers through Near-Field Electrospinning and Photopolymerization} % Main chapter title

\label{Chapter:5}

@@

%Were the selected candidates electrospunable?
%Fiber morphology

### 2020-05-28 myThesis/thesis_LaTeX/Chapters/6.tex
thesis  structure
thesis re-organisation

\chapter{Fabrication of Polymeric Fibers through Near-Field Electrospinning and Photopolymerization} % Main chapter title

\label{Chapter:5}

@@

Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

>>>>

\chapter{Fabrication of Conductive Carbon nanofibers by Pyrolysis of Polymeric Fibers} % Main chapter title

\label{Chapter:6}

@@

%Yield rate
%Carbon content
%Conductivity
%Fiber morphology

### 2020-05-28 myThesis/thesis_LaTeX/Chapters/7.tex
thesis  structure
thesis re-organisation

\chapter{Fabrication of Conductive Carbon nanofibers by Pyrolysis of Polymeric Fibers} % Main chapter title

\label{Chapter:6}

%----------------------------------------------------------------------------------------
%	SECTION 1
%----------------------------------------------------------------------------------------
\section{}

Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

>>>>

\chapter{Comparison of the Carbon Fibers Obtained Against SU8-based Carbon Fibers} % Main chapter title

\label{Chapter:7}

%----------------------------------------------------------------------------------------
%	SECTION 1
%----------------------------------------------------------------------------------------
\section{Fabrication and Characterization of Legacy SU-8 carbon fibers}
